---
title: "Tourism Charts"
author: "David Alexander"
date: "03/01/2020"
output: html_document
---

### Introduction
This page contains the data and analysis of all the charts in the Tourism State of the Park paper. The data tables are printed out so the underlaying data can be seen. 

This data is processed using the https://www.tidyverse.org/packages/ packages in R

```{r setup, include=FALSE}
## Set Wd 
setwd("~/GitHub/stateoftheparkcontent")
## Load tidyverse
library(tidyverse)
library(plotly)
library(kableExtra)
```

### Figure 1: STEAM Volume of visits in Visitor Days and Visitor Numbers 2009-2018
* **Data Source:** STEAM model Peak District and Influence Area https://www.globaltourismsolutions.co.uk/steam-model/

* **Next Updated:** Autumn 2020

```{r, message=FALSE}
# Read the data
fig1 <- read_csv("Tourism_Data/Figure_1.csv")
# View the data
as_tibble(fig1)
```

```{r}
# plot a graph 
fig1_p <- ggplot(data = fig1, aes(x=Year, y=Millions, fill=Visit_Type)) +
  geom_bar(stat = "identity", position=position_dodge()) +
  scale_fill_manual(values=c("#999999", "#8d395b")) +
  xlab("Year") + ylab("Millions (000's)") +
  ggtitle("Figure 1: STEAM Volume of visits in Visitor Days & Visitor Numbers 2009-2018") +
  coord_cartesian(xlim =c(2009, 2018)) +
  theme_minimal()

# output a plot
ggplotly(fig1_p) %>%
  layout(legend = list(orientation = "h", x = 0.4, y = -0.2))
```

#### Figure 2: STEAM Volume of visits in Visitor Days per month (Year 2018)
* **Data Source:** STEAM model Peak District and Influence Area https://www.globaltourismsolutions.co.uk/steam-model/

* **Next Updated:** Autumn 2020

```{r, message=FALSE}
# read data
fig2 <- read_csv("Tourism_Data/Figure_2.csv")

# order a factor for plotting
fig2$Month <- factor(fig2$Month, levels = month.abb)

# View the data
as_tibble(fig2)
```

```{r}
# plot a graph 
fig2_p <- ggplot(data = fig2, aes(x=Month, y=Visitor_Days, group=1)) +
  geom_line(colour = "#8d395b") +
  xlab("Month 2018") + ylab("Visitor Days") +
  ggtitle("Figure 2: STEAM Volume of visits in Visitor Days per month 2018") +
  theme_minimal()

# output a plot
ggplotly(fig2_p)
```

#### Figure 3: STEAM Sectoral Distribution of Economic Impact; Tourist Expenditure (£Million 2009-2018 VAT indexed 2017)
* **Data Source:** STEAM model Peak District and Influence Area https://www.globaltourismsolutions.co.uk/steam-model/

* **Next Updated:** Autumn 2020

| SECTOR               | 2009 | 2010 | 2011 | 2012 | 2013 | 2014 | 2015 | 2016 | 2017 | 2018 |
|----------------------|------|------|------|------|------|------|------|------|------|------|
| ACCOMMODATION        | £76  | £80  | £78  | £78  | £79  | £81  | £78  | £77  | £82  | 2017 |
| FOOD & DRINK         | £94  | £92  | £93  | £91  | £90  | £93  | £94  | £94  | £100 | 2017 |
| RECREATION           | £37  | £36  | £37  | £36  | £35  | £36  | £37  | £37  | £40  | 2017 |
| SHOPPING             | £116 | £112 | £115 | £111 | £110 | £113 | £115 | £116 | £125 | 2017 |
| TRANSPORT            | £51  | £50  | £50  | £49  | £49  | £50  | £50  | £51  | £54  | 2017 |
| DIRECT REVENUE       | £373 | £370 | £373 | £365 | £364 | £373 | £374 | £374 | £400 | 2017 |
| VAT                  | £56  | £65  | £75  | £73  | £73  | £75  | £75  | £75  | £80  | 2017 |
| DIRECT EXPENDITURE   | £429 | £434 | £447 | £438 | £437 | £448 | £448 | £449 | £481 | 2017 |
| INDIRECT EXPENDITURE | £146 | £147 | £151 | £148 | £147 | £151 | £151 | £152 | £163 | 2017 |
| TOTAL                | £575 | £581 | £599 | £585 | £584 | £599 | £600 | £602 | £644 | 2017 |


#### Figure 4: Economic Activity Visitor Survey 2015
* **Data Source:** Peak District National Park Visitor Survey 2014/15

* **Next Updated:** TBC 

```{r, message=FALSE}
# read data
fig4 <- read_csv("Tourism_Data/Figure_4.csv")

# View the data
as_tibble(fig4)
```

```{r}
colors <- c('rgb(141,57,91)', 'rgb(128,133,133)', 'rgb(144,103,167)', 'rgb(171,104,87)','rgb(114,147,203)','rgb(144,103,167)', 'rgb(171,104,87)', 'rgb(114,147,203)')

fig4_p <- plot_ly(fig4, labels = ~Economic_Activity, values = ~Percentage, type = 'pie',
        textposition = 'inside',
        textinfo = 'label+percent',
        insidetextfont = list(color = '#FFFFFF'),
        hoverinfo = 'text',
        text = ~paste(Economic_Activity, Percentage * 100,'%'),
        marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)),
                      #The 'pull' attribute can also be used to create space between the sectors
        showlegend = FALSE) %>%
  layout(title = 'Figure 4: Economic Activity Visitor Survey 2015',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

# output a plot
ggplotly(fig4_p)
```

#### Figure 5: Group Size Visitor Survey 2015 
* **Data Source:** Peak District National Park Visitor Survey 2014/15

* **Next Updated:** TBC 
```{r, message=FALSE}
# Read the data
fig5 <- read_csv("Tourism_Data/Figure_5.csv")
# View the data
as_tibble(fig5)
```

```{r}
# plot a graph 
fig5_p <- plot_ly(fig5, x = ~Group_Size, y = ~Percentage, type = 'bar', color = I("#8d395b")) %>%
  layout(title = "Figure 5: Group Size Visitor Survey 2015 ",
         xaxis = list(title = "Group Size"),
         yaxis = list(title = "Percentage"))

# output a plot
fig5_p
```

#### Figure 6: Visitor Origin by Region
* **Data Source:** Peak District National Park Visitor Survey 2014/15
* **Data Source:** http://geoportal.statistics.gov.uk/datasets/4fcca2a47fed4bfaa1793015a18537ac_4

* **Next Updated:** TBC
```{r, message=FALSE}
# Load the extra libraries for maping 
library("GISTools")
RegionSP <- readShapePoly("~/GitHub/stateoftheparkcontent/Tourism_Data/SP/Regions_December_2017_Ultra_Generalised_Clipped_Boundaries_in_England.shp")
# Read the data
fig6 <- read_csv("Tourism_Data/Figure_6.csv")
# View the data
##################as_tibble(fig6)
```

```{r, message=FALSE}
# Load the extra Libraries
library(cartogram)
library(tmap)
#library(broom)
# Merge the data to the SP boundary
RegionSP <- merge(RegionSP, fig6, by.x="rgn17nm", by.y="Region")

#Create Cartogram & Choropleth
fig6_p <- cartogram(RegionSP, "Percentage", itermax=7)

tm_shape(fig6_p) + tm_polygons("Percentage", style = "jenks", palette = "PuRd") +
  tm_layout(frame = FALSE, legend.position = c("left", "top"))

```


#### Figure 7: Knowledge about the Peak District 
* **Data Source:** Peak District National Park Non Visitor Survey 2014/15

* **Next Updated:** TBC 
```{r, message=FALSE}
# Read the data
fig7 <- read_csv("Tourism_Data/Figure_7.csv")
# View the data
as_tibble(fig7)
```

```{r}
# plot a graph 
fig7_p <- plot_ly(fig7, x = ~Knowledge, y = ~Percentage, type = 'bar', color = I("#8d395b")) %>%
  layout(title = "Figure 7: Knowledge about the Peak District",
         xaxis = list(title = "Knowledge about the Park", tickangle = -0),
         yaxis = list(title = "Percentage"))

# output a plot
fig7_p
```

#### Figure 8: Likelihood to visit the National Park in the future
* **Data Source:** Peak District National Park Visitor Survey 2014/15

* **Next Updated:** TBC 
```{r, message=FALSE}
# Read the data
fig8 <- read_csv("Tourism_Data/Figure_8.csv")
# View the data
as_tibble(fig8)
```

```{r}
# plot a graph 
fig8_p <- plot_ly(fig8, x = ~Likelihood, y = ~Percentage, type = 'bar', color = I("#8d395b")) %>%
  layout(title = "Figure 8: Likelihood to visit the National Park in the future",
         xaxis = list(title = "Likelihood to visit the Park"),
         yaxis = list(title = "Percentage"))

# output a plot
fig8_p
```

#### Figure 9: ACORN Results: Proportion of postcodes per ACORN Category 
* **Data Source:** Peak District National Park Non / Visitor Survey 2014/15
* **Data Source:** https://acorn.caci.co.uk/

* **Next Updated:** TBC 

```{r, message=FALSE}
# Read the data
fig9 <- read_csv("Tourism_Data/Figure_9.csv")
# View the data
as_tibble(fig9)
```
```{r}
kable(fig9) %>%
  kable_styling(bootstrap_options = "striped", "condensed", full_width = F)
```

#### Figure 10: Figure 10: Monthly Visitor Centre Contacts 2018
* **Data Source:** Peak District National Park Authority

* **Next Updated:** Autumn 2020
```{r, message=FALSE}
# read data
fig10 <- read_csv("Tourism_Data/Figure_10.csv")

# order a factor for plotting
fig10$Month <- factor(fig10$Month, levels = month.abb)

# View the data
as_tibble(fig10)
```

```{r}
# plot a graph 
fig10_p <- ggplot(data = fig10, aes(x=Month, y=Contacts, group=1)) +
  geom_line(colour = "#8d395b") +
  xlab("Month") + ylab("Number of Contacts") +
  ggtitle("Figure 10: Figure 10: Monthly Visitor Centre Contacts 2018") +
  theme_minimal()

# output a plot
ggplotly(fig10_p)
```

#### Figure 11: Average 2000-2018 of all Contacts at TICs
* **Data Source:** STEAM model Peak District and Influence Area https://www.globaltourismsolutions.co.uk/steam-model/

* **Next Updated:** Autumn 2020
```{r, message=FALSE}
# Read the data
fig11 <- read_csv("Tourism_Data/Figure_11.csv")
# View the data
as_tibble(fig11)
```

```{r}
kable(fig11) %>%
  kable_styling(bootstrap_options = "striped", "condensed", full_width = F)
```

#### Figure 12: Cyclists & Walkers 2 way counts Hassop Station Monsal Trail 2017
* **Data Source:** Peak District National Park Authority

* **Next Updated:** Autumn 2020
```{r, message=FALSE}
# read data
fig12 <- read_csv("Tourism_Data/Figure_12.csv")

# order a factor for plotting
fig12$Month <- factor(fig12$Month, levels = month.abb)

# View the data
as_tibble(fig12)
```

```{r}
# plot a graph 
fig12_p <- ggplot(data = fig12, aes(x=Month, y=Count, group=Mode)) +
  geom_line(colour = "#8d395b") +
  xlab("Month") + ylab("Number") +
  ggtitle("Figure 12: Cyclists & Walkers 2 way counts Hassop Station Monsal Trail 2017") +
  theme_minimal()

# output a plot
ggplotly(fig12_p)
```


#### Figure 13: Serviced Accommodation 2017 STEAM Bed Spaces
* **Data Source:** STEAM model Peak District and Influence Area https://www.globaltourismsolutions.co.uk/steam-model/

* **Next Updated:** Autumn 2020
```{r, message=FALSE}
# Read the data
fig13 <- read_csv("Tourism_Data/Figure_13.csv")
# View the data
as_tibble(fig13)
```

```{r}
kable(fig13) %>%
  kable_styling(bootstrap_options = "striped", "condensed", full_width = F)
```


#### Figure 14: Non-Serviced Accommodation 2017
* **Data Source:** STEAM model Peak District and Influence Area https://www.globaltourismsolutions.co.uk/steam-model/

* **Next Updated:** Autumn 2020
```{r, message=FALSE}
# Read the data
fig14 <- read_csv("Tourism_Data/Figure_14.csv")
# View the data
as_tibble(fig14)
```

```{r}
kable(fig14) %>%
  kable_styling(bootstrap_options = "striped", "condensed", full_width = F)
```

#### Figure 15: Seasonal Availability of bed supply STEAM 2018
* **Data Source:** STEAM model Peak District and Influence Area https://www.globaltourismsolutions.co.uk/steam-model/

* **Next Updated:** Autumn 2020
```{r, message=FALSE}
# Read the data
fig15 <- read_csv("Tourism_Data/Figure_15.csv")
# View the data
as_tibble(fig15)
```

```{r}
# plot a graph 
fig15_p <- ggplot(data = fig15, aes(x=Month, y=Count, fill=Type)) +
  geom_bar(stat = "identity", position="stack") +
  scale_fill_manual(values=c("#999999", "#8d395b")) +
  xlab("Month") + ylab("Bed Supply") +
  ggtitle("Figure 15: Seasonal Availability of bed supply STEAM 2018") +
  theme_minimal()

# output a plot
ggplotly(fig15_p) %>%
  layout(legend = list(orientation = "h", x = 0.4, y = -0.2))
```







